---
title: "Data 607 Week 9"
author: "Maryluz Cruz"
date: "10/26/2019"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment

The New York Times web site provides a rich set of APIs, as described here: https://developer.nytimes.com/apis
You’ll need to start by signing up for an API key.
Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame.

## Load the Packages
```{r warning=FALSE, message= FALSE}
require(jsonlite)
require(dplyr)
require(kableExtra)
```


## Input API Key
```{r warning=FALSE, message= FALSE, include=FALSE}
moviekey<-"api-key=aJyfCJwQ9Yovsz66QAvp7gheqAFqgpz7" 
```
API-Key is Hidden

## Add the URL 
```{r warning=FALSE, message= FALSE}

url<-"https://api.nytimes.com/svc/movies/v2/reviews/search.json?query=godfather&"
```


Here we put the API key and the link together. 
```{r warning=FALSE, message= FALSE}
movies<-fromJSON(paste0(url,moviekey))
```


## Transform into a DataFrame 
```{r warning=FALSE, message= FALSE}
movies1<-as.data.frame(movies$results)

colnames(movies1)
```


```{r warning=FALSE, message= FALSE}
movies1
```

Remove Columns 
```{r warning=FALSE, message= FALSE}
movies2 <-movies1[c(1:2,4:7)]

```


## Final Table 
```{r warning=FALSE, message= FALSE}
colnames(movies2)<-c("Title", "Rating","Actors","Headline","Summary","Pub_Date")

kable(movies2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```